Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-22 demystify.tex
updates

A common question is whether you should mention, e.g., in your SOP, that you are a member of an underrepresented and minority (URM) group\footnote{URM in CS in the US include African Americans, Hispanic Americans, American Indians/Native Alaskans, Native Hawaiians/Pacific Islanders (excluding Asian Americans), and multiracial students identifying with at least one of the previously listed URM categories.} or LGBTQ+ group.
The main concern is that mentioning this might make you look like you are asking for special treatment or that you might get discriminated against.

@@

  \item[RA and TA] Research Assistantship (RA) is form of funding where you work on a research project for a professor. Teaching Assistantship (TA) is a form of funding where you help a a professor with teaching (e.g., grading assignments).

>>>>

A common question is whether you should mention, e.g., in your SOP, that you are a member of an underrepresented and minority (URM) group\footnote{URM in CS in the US include African Americans, Hispanic Americans, American Indians/Native Alaskans, Native Hawaiians/Pacific Islanders (excluding Asian Americans), and multiracial students identifying with at least one of the previously listed URM categories.} or LGBTQ+ group.
The main concern is that you can be discriminated against or that you are asking for special treatment.

@@

  \item[RA and TA] Research Assistantship (RA, \autoref{sec:ra}) is a funding where you work on a research project for a professor. Teaching Assistantship (TA, \autoref{sec:ta}) is a funding where you help a a professor with teaching (e.g., grading assignments).
